### 2019-12-10 ack.tex
update acks

\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}

@@

between ingenuity and completely insane.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}

@@

\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Joeri, we've come full circle. You started me on this adventure

@@

If we were genes, I'm sure we would reciprocal activators,

@@

Thanks for putting so many healthy vege-tables and strange Polish delicacies in our fridge,

@@

\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Soup: Dani, Helena, Caroline, Robin B, Maxim, Annelies, Quentin, Katrien, Arne G, Ruth, Joris
Dambi
Dambi
Dambi
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Miriam
Miriam
Miriam
Miriam
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Laure, Michael, Jasper en Lize (spelling??)
Mara, Seppe \& Alice
Marta, Jan, Tristan, Rafael

@@

\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Cedric
Cedric
Cedric
Cedric
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Familie
Familie
Familie
Familie
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Victor, humor
Victor
Victor
Victor
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Hendrik, getting into PC
Hendrik 
Hendrik
Hendrik
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Papa Chris, babbel voor het slapen gaan, de vele schaakspelletjes
Chris
Chris
Chris
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Mama en papa Jean-Paul: opvoeding, zorgeloosheid
Mama
Mama
Mama
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}
Amor, as I write this, you are sitting on my lap and drooling on the table.
I guesstimate about 50\% of this dissertation was written like this.
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}

@@

Remi
Remi
Remi
\rule{10cm}{0.4pt}
\rule{10cm}{0.4pt}

@@

>>>>

\newperson
\newperson

@@

between ingenuity and complete insanity.
\newperson
\newperson

@@

\newperson
\newperson
Joeri, we've come full circle. You brought me into this whole adventure

@@

If we were genes, I'm sure we would be reciprocal activators,

@@

Thanks for putting so many healthy “vege-tables” and strange Polish delicacies in our fridge,

@@

\newperson
\newperson
A big thank you to all the Dambini's for taking care of me while I was hard at work:
An,ArS,ArG,Art,C,D,H,I,Ja,Jon,Jor,Ka,Ke,Li,Lo,M,N,Pa,Pi,Q,RVd,RB,Ru,Sa,Sl,So,St,W,Y.
I'm grateful to be part of such a dynamic and fun group;
you all make hard work at the VIB feel like a walk in the park.
\newperson
\newperson
Miriam, thanks for always being there for us, 
during the good times but also during times of need.
As part of our family, there will always be a spot for you in our house.
Let it be a while until one of us has to organise another reception.
\newperson
\newperson
Because relaxing is as important as work,
a special thanks to a selection of the finest friends.
Laure, Michael, Jasper \& Lize for haut cuisine fun veggie nights.
Joke, Niels \& Kai for exploring dungeons with trolls and lizards together.
Marta, Jan, Tristan \& Rafaël for the many tasty brunches and classy parties.
Mara Marrainne, Sepperd \& Alice for all the unforgettable family moments with our cute kids.

@@

Sophie and Marc for entertaining Caro while Elias, Charlotte and I play Minecraft together.
\newperson
\newperson
Cedric, no time difference or distance can keep us apart,
or change our habit to forget the world during our gaming and conversations. 
놀라운 사람과 최고의 친구가되어 주셔서 감사합니다
\newperson
\newperson
My warm thoughts go to:
Vanessa, Marilou, Franco, Alain, Luc, Malika, Sien, Silke, Liam
Anne, Patrick, Evelyne, Stefaan, Steven, Joke, Paul, Tania, Arne, Laure, Lukas, Lise, Dorian
\newperson
\newperson
To mama and papa Jean Paul, thank you for all your love.
You gave me a carefree youth and a good set of morals,
and allowed me to study for as long as I liked.
For all these things and so much more, I can never repay you.
\newperson
\newperson
Papa Chris, I always enjoy talking to you, such as the countless
chess games that we played, and the late night discussions by my bedside.
You made me think for myself and have an opinion of my own.
At the right time, I will pass on the torch to Remi.
\newperson
\newperson
Victor, you're the most adventurous of us three brothers.
Maybe you don't know yet what life will bring, and that's okay. None of us do.
I enjoy driving other people absolutely nuts with our crazy talk.
Thanks for all the memes :)
\newperson
\newperson
Hendrik, as the one who I always looked up to, I blame you for getting me interested
in computers. With you taking computers apart on the table, how could I resist.
I know you paid dearly for this, though, since you would continuously have to
repair the \textit{Windows Me} installation that I just destroyed.
\newperson
\newperson
Ingeborg, Elke and Gallina, thank you for your hospitality and tasty food.
You are all amazing women
for all I know, dealing with a Cannoodt,
requires a special kind of patience.
\newperson
\newperson
To Amor, a big thank you for contributing countless cuddles and endless drool.
I guesstimate at least 50\% of the dissertation was written with you on my lap.
\newperson
\newperson

@@

You're only seven months old, but it feels like I've known you for much longer already.
Your spontaneous happiness when you see me come downstairs 
from a hard day of work immediately makes my day.
\newperson
\newperson

@@

1
